\section{Referências} % Seções são adicionadas para organizar sua apresentação em blocos discretos, todas as seções e subseções são automaticamente exibidas no índice como uma visão geral da apresentação, mas NÃO são exibidas como slides separados.

\begin{frame}{Principais referências}
    \footnotesize
    \begin{thebibliography}{99}
        \bibitem{autorartigo} ASHTIANI, M. N.; RAAHEMI, B. \textit{News-based intelligent prediction of financial markets using text mining and machine learning: A systematic literature review}. Expert Systems with ApplicationsElsevier Ltd, 1 maio 2023.
        \medskip
        \bibitem{autorartigo} MAO, Y.; LIU, Q.; ZHANG, Y. \textit{Sentiment analysis methods, applications, and challenges: A systematic literature review}. Journal of King Saud University - Computer and Information SciencesKing Saud bin Abdulaziz University, , 1 abr. 2024.
        \medskip
        \bibitem{autorartigo} SOLAIMAN, S. et al. \textit{Unveiling Market Sentiments: A Comprehensive Analysis of Stock Market Responses to Diverse News Events Using Data Mining Techniques}. Proceedings of the 2024 18th International Conference on Ubiquitous Information Management and Communication, IMCOM 2024. Institute of Electrical and Electronics Engineers Inc., 2024. 
        \medskip
        \bibitem{autorartigo} SINDHU, B. et al. \textit{The Evolution of Large Language Model: Models, Applications and Challenges}. Proceedings - 2024 International Conference on Current Trends in Advanced Computing, ICCTAC 2024, 2024. 
    \end{thebibliography}
    
\end{frame}

\begin{frame}{Principais referências}
    \footnotesize
    \begin{thebibliography}{99}
        \bibitem{autorartigo} CHAHAR, R.; DUBEY, A. K. \textit{Machine learning-based Sentiment Analysis: A Comprehensive Review}. 2024 International Conference on Cognitive Robotics and Intelligent Systems, ICC - ROBINS 2024, p. 52–57, 2024.
        \medskip
        \bibitem{autorartigo} JIN, X.; CHEN, C.; YANG, X. \textit{The effect of international media news on the global stock market}. International Review of Economics and Finance, v. 89, p. 50–69, 1 jan. 2024.
        \medskip
        \bibitem{autorartigo} SANTOS, L. L.; BIANCHI, R. A. C.; COSTA, A. H. R. \textit{FinBERT-PT-BR: Análise de Sentimentos de Textos em Português do Mercado Financeiro FinBERT-PT-BR}. Journal of the Brazilian Computer Society, 6 ago. 2023.
        \medskip
        \bibitem{autorartigo} TABINDA KOKAB, S.; ASGHAR, S.; NAZ, S. \textit{Transformer-based deep learning models for the sentiment analysis of social media data}. Array, v. 14, 1 jul. 2022. 
    \end{thebibliography}
\end{frame}
